Response to reviewers

### 2016-10-25 revision/response2.Rmd
Typo fixes and response rebuilding

---
title: "Response to reviewers"
author: "Eric Hare, Heike Hofmann, Alicia Carriquiry"
date: "October 17, 2016"
output:
  pdf_document: default
bibliography: references.bib
---

@@

1. The authors have not provided a comprehensive literature review, to the point that the paper appears to be taking credit for the work that has been done by Dr. Nick Petraco, his collaborators, and others. I provided the references for Dr. Petraco’s work in my last review.

    **Please see the attached document for an in-depth discussion of our use of Dr. Petraco's work**

@@

    **On October 11th, 2016, we sat down with Dr. Morris in order to discuss the similarities and differences between the Chumbley U-statistic, and the methods used and features derived in our paper. He was surprised to see this comment, as the differences are rather stark. The Chumbley U-statistic characterizes toolmark signatures by producing two sets of correlation values. One set is produced by doing "coordinated shifts" after finding the ideal matching window, and computing each correlation value. The other set is computed by doing "independent shifts". Given that two toolmarks match, we'd expect that the correlation values from the coordinated shifts would be significantly higher than the independent shifts, and this is assessed using a Mann-Whitney U statistic. While very interesting and worth further discussion, Dr. Morris agreed that this is far different from the methods we have proposed. We use full pairs bullet signatures and extract features based on these. The features including correlation, as well as the number of matches, the number of consecutive matches, and more. At no time is a Mann-Whitney U statistic used, windows extracted, or any coordinated/independent shifts used.**

@@

    **Please see the attached document for a rebuttal to these claims**

@@

    **XXX**

@@

    **XXX**

@@

    **XXX**

@@

    **We are very clear about the limitations presented by a small dataset, particularly in the conclusion. Unfortunately, this is the data that we had to work with. With that said, the idea of statistical modeling is that once new data is obtained, its rather trivial to compute the set of features used in our model, and retrain the model with a broader and more varied dataset. Whether performance on holdout samples would remain as strong remains to be seen. But because this code is open-source and in the public domain, the algorithm can be assessed on new data by anyone willing to invest the time to run it.**

@@

    **We feel this is a rather inaccurate summary of the work done in our paper. We do use a random forest model, but this is not the focus. Rather, the data analysis steps culminating in feature extraction are the focus. These features, computed on pairs of bullet lands, are then fed into a random forest model, but we do formulate this model. Furthermore, we do not perform a version of least squares - The random forest uses decision trees. We felt the purpose of our work was to highlight the individual data analysis steps that compromise a full analysis of bullet striations, beginning from an open-source data file, and ending with a predicted probability of a match.**

@@

    **The revised copy of our paper contains over thirty references, not just one. Many are from previous statistical studies on bullet matching (e.g., Biasotti 1959, Chu 2010, Riva 2014) while many more are references on statisitcal tests themselves (e.g., Therneau 2015, Liaw 2002, Cleveland 1979)**

@@

    **XXX**

@@

@@

## x3prplus

>>>>

---
title: "Response to reviewers"
author: "Eric Hare, Heike Hofmann, Alicia Carriquiry"
date: "October 24, 2016"
output:
  pdf_document: default
bibliography: references.bib
---

@@

1. The authors have not provided a comprehensive literature review, to the point that the paper appears to be taking credit for the work that has been done by Dr. Nick Petraco, his collaborators, and others. I provided the references for Dr. Petraco's work in my last review.

    **Most of the references that were suggested by reviewers earlier were incorporated into the revised version of the manuscript.  Regarding the "overlap" with Petraco's work, please see the attached document entitled x3prplus for an in-depth discussion of our use of exactly one function in Petraco's package.**

@@

    **First, it seems more appropriate to refer to Hoeksema's U statistic since she was the one to propose its use in her dissertation.  As the reviewer notes, this work was carried out in our own department, and we were well aware of it.  Thus our surprise with the review, since to say that our work is a repeat of Amy Hoeksema's work is so inaccurate as to make us wonder whether the reviewer is familiar with either approaches.  On October 11th, 2016, we sat down with Max Morris to discuss the similarities and differences between the Hoeksema U-statistic, and the methods used and features derived in our paper. Max was at least as surprised as we were to read the reviewer's comment, since the differences between Amy's work and ours are stark. The Hoeksema U-statistic characterizes toolmark signatures by producing two sets of correlation values. One set is produced by doing "coordinated shifts" after finding the ideal matching window, and computing each correlation value. The other set is computed by doing "independent shifts". When the two toolmarks match, we'd expect that the correlation values from the coordinated shifts would be significantly higher than those computed from the independent shifts, and this is assessed using a Mann-Whitney U statistic. While very interesting and worth further discussion, Max Morris agreed that this is far different from the methods we have proposed. In our work, we use full bullet signatures from pairs of bullets and extract several features based on these. The features include a cross-correlation, as well as the number of matching striae, the number of consecutive matching striae, the difference in the height of the signatures at each peak and at each valley, and several more. At no time is a Mann-Whitney U statistic used, windows extracted, or any coordinated/independent shifts used. These are completely different approaches where the only "similarity" is that we also compute a correlation, albeit between different variables!**

@@

    **The reviewer must have looked at the wrong code because no one who is reasonably familiar with R would claim that x3prplus is a "wrapper" for x3pr!  Please see the attached document for a rebuttal to these claims.  In x3prplus, all we did is call ONE of Petraco's functions, read.x3p, to read 3D files.  Everything else is completely different, as can be seen in the attached document. Perhaps our choice of name for the package has contributed to the confusion.**

\newpage

@@

    **We thank the reviewer for his/her lecture, but it is difficult to take his/her comments seriously when they are offered with absolutely no evidence.  Exactly whose work are we re-inventing? And where has work similar to ours been published?  If the reviewer is going to make statements such as the ones above, please, try to back them up with some facts.**

@@

    **Really?  We have referred to many of those papers in the manuscript and have shown how our approach is quite different.  Indeed, even PCAST (the President's Council of Advisors in Science and Technology) in its report, mentioned that our work was the only promising work and they actually looked at all the literature themselves. So we respectfully disagree with Reviewer 2. The Riva and Champod paper published in 2014 is indeed referred to in the manuscript and of all the published work, it is the one that most resembles what we have done.  The reviewer poo-poos our saying that one difference is that Riva and Champod worked on casings and we worked on bullets.  The reviewer would be well advised to read our comment more carefully;  the reason it is important is that Riva and Champod make use of the circular structure of their data to pre-process their images and develop their score.  A big component of their algorithm is the alignment of images, which they do by rotating the images on the xY plane.  This is not something that cannot be extended to the case of bullets, were the XY plane is not flat and where rotation makes no sense.  The approach they use to extract features from the aligned images is completely different from ours and for the reviewer to say that we are re-inventing the wheel is a bit of a scandal.  The fact that Riva and Champod have come up with a nice automated algorithm to match breech face and firing pin images does not mean that we cannot come up with a DIFFERENT automated algorithm to match bullet lands. This said, we have added additional commentary about Riva and Champod in our manuscript.**

@@

    **Again, we have to disagree with the reviewer and again we take issue at his/her bandying about such incendiary comments with nothing to back them up.  We are not confused, in particular not on the issue of inference.  In the intro we mentioned the type of inference that is often drawn in legal settings, mostly to satisfy an earlier reviewer (an actual constructive reviewer) who requested that we add a bit of general background in the introduction.  We then proceed to explain that this is not what we pursue in our paper;  all we want to present is an automated algorithm to decide whether two bullets may have been fired from the same gun.  No more and no less.  Yes, we are focusing on error rates, and for the reviewer's peace of mind, yes, we realize that there is a decision implicit in our trying to compute an error rate.  The decision is simply whether two bullets may have been fired from the same gun.  We have gone back to the manuscript and added some additional language to explain the purposes of the work we present.**

@@

    **We are very clear about the limitations presented by a small dataset, particularly in the conclusion. Unfortunately, this are the data that we had to work with. With that said, the idea of statistical modeling is that once new data are obtained, it will be rather trivial to compute the set of features used in our model, and retrain the model with a broader and more varied dataset. Whether performance on holdout samples would remain as strong remains to be seen. But because this code is open-source and in the public domain, the algorithm can be assessed on new data by anyone willing to invest the time to run it. While the dataset is small (only 10 barrels) we have been told by multiple firearm examiners that it is a challenging dataset on which to develop methods because the 10 barrels were consecutively manufactured. Thus, one would expect that thre striae made by those barrels will be more similar across them than across two randomly selected barrels from a large population. We are collaborating with Alan Zhang in NIST to assemble a larger database that will be publicly available within a year or two.**

\newpage

@@

    **We feel this is a rather inaccurate summary of the work done in our paper. We do use a random forest model, but this is not the focus. Rather, the data analysis steps culminating in feature extraction are the focus. These features, computed on pairs of bullet lands, are then fed into a random forest model, but we do formulate this model. Furthermore, we do not perform a version of least squares - The random forest uses decision trees. (Is the reviewer thinking of regression trees?  If so, that is not what we are implementing.) One purpose of our work is to highlight the individual data analysis steps that compromise a full analysis of bullet striations, beginning from an open-source data file, and ending with a predicted probability of a match.**

@@

    **Did the reviewer read the correct paper?  The revised copy of our paper contains over thirty references, not just one. Many are from previous statistical studies on bullet matching (e.g., Biasotti 1959, Chu 2010, Riva 2014) while many more are references on statisitcal tests themselves (e.g., Therneau 2015, Liaw 2002, Cleveland 1979)**

@@

    **We believe that the focus on a timely application and the novel combination of statistical and machine learning methods to address the problem warrant publication in the Annals of Applied Statistics.**

\newpage

@@

\newpage

@@

\newpage

# x3prplus
